### 2018-09-18 README.Rmd
update readme

> A comparison of single-cell trajectory inference methods: towards more accurate and robust tools  
<strong> Wouter Saelens\* </strong> <a href='https://orcid.org/0000-0002-7114-6248'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/orcid_logo.svg?sanitize=true' height='16'></a> <a href='https://github.com/zouter'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/github_logo.png' height='16'></a>,
<strong> Robrecht Cannoodt\* </strong> <a href='https://orcid.org/0000-0003-3641-729X'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/orcid_logo.svg?sanitize=true' height='16'></a> <a href='https://github.com/rcannood'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/github_logo.png' height='16'></a>,
Helena Todorov <a href='https://github.com/Helena-todd'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/github_logo.png' height='16'></a>,
<em> Yvan Saeys </em> <a href='https://github.com/saeyslab'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/github_logo.png' height='16'></a>  
[bioRxiv:276907](https://www.biorxiv.org/content/early/2018/03/05/276907) [doi:10.1101/276907](https://doi.org/10.1101/276907)

>>>>

```{r}
get_altmetric_badge <- function() {
  curl::curl_fetch_memory("https://api.altmetric.com/v1/doi/10.1101/276907")$content %>%
    rawToChar() %>% 
    jsonlite::fromJSON() %>% 
    purrr::pluck("images") %>%
    purrr::pluck("medium") %>% 
    paste0("&style=bar")
}
```

> A comparison of single-cell trajectory inference methods: towards more accurate and robust tools  
<strong> Wouter Saelens\* </strong> <a href='https://orcid.org/0000-0002-7114-6248'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/orcid_logo.svg?sanitize=true' height='16'></a> <a href='https://github.com/zouter'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/github_logo.png' height='16'></a>,
<strong> Robrecht Cannoodt\* </strong> <a href='https://orcid.org/0000-0003-3641-729X'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/orcid_logo.svg?sanitize=true' height='16'></a> <a href='https://github.com/rcannood'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/github_logo.png' height='16'></a>,
Helena Todorov <a href='https://github.com/Helena-todd'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/github_logo.png' height='16'></a>,
<em> Yvan Saeys </em> <a href='https://github.com/saeyslab'><img src='https://github.com/dynverse/dynmethods/raw/master/man/figures/github_logo.png' height='16'></a>  
[bioRxiv:276907](https://www.biorxiv.org/content/early/2018/03/05/276907) [doi:10.1101/276907](https://doi.org/10.1101/276907) [![altmetric](`r get_altmetric_badge()`)](https://altmetric.com/details/33972849)
